The Astropy Project:

### 2017-09-29 main.tex
use a description list for key new features

The \texttt{astropy.coordinates} subpackage is designed to support representing
and transforming celestial coordinates and, new in version 2.0, velocities.
The framework heavily relies on the \texttt{astropy.units} subpackage, and most
inputs to objects in this subpackage are expected to be \texttt{Quantity}
objects.
A key concept behind the design of this subpackage is that coordinate
\textit{representations} and \textit{reference systems / frames} are independent
of one another.
For example, a set of coordinates in the International Celestial Reference
System (ICRS) reference frame could be represented as a spherical (distance,
right ascension, declination) or Cartesian coordinates.
They can therefore be re-represented or transformed to other reference frames
(e.g., the Galactic frame) in an independent way.

@@

\textbf{Key new features:}
\begin{itemize}
    \item In addition to representing celestial coordinates, \astropypkg\
    now supports specifying positions on the Earth in a number of different
    geocentric systems with the \texttt{EarthLocation} class.
    With this, \astropypkg\ now supports Earth-location-specific coordinate
    systems such as the altitude-azimuth (\texttt{AltAz}) or horizontal system.
    Transformations between \texttt{AltAz} and any Barycentric coordinate frame
    also requires specifying a time using the \texttt{Time} class from
    \texttt{astropy.time}.
    With this new functionality, many of the common tasks associated with
    observation planning can now be completed with \astropypkg\ or the
    \astropy-affiliated package \texttt{astroplan} (TODO: cite zenodo entry?).
    \item TODO: differential classes. Represent single-derivatives of
    representations. Used to store velocity information, only really useful
    attached to a representation object.
    \item TODO: Frame classes support proper motions, radial velocities. Explain
    component naming, why SkyCoord doesn't support right now, "experimental" but
    tested feature.
    \item TODO: JPL ephemerids % Who can write this? Erik?
\end{itemize}

>>>>

\subsubsection{Overview}
The \texttt{astropy.coordinates} subpackage is designed to support representing
and transforming celestial coordinates and, new in version 2.0, velocities.
The framework heavily relies on the \texttt{astropy.units} subpackage, and most
inputs to objects in this subpackage are expected to be \texttt{Quantity}
objects.
A key concept behind the design of this subpackage is that coordinate
\textit{representations} and \textit{reference systems / frames} are independent
of one another.
For example, a set of coordinates in the International Celestial Reference
System (ICRS) reference frame could be represented as a spherical (distance,
right ascension, declination) or Cartesian coordinates.
They can therefore be re-represented or transformed to other reference frames
(e.g., the Galactic frame) in an independent way.

@@

\subsubsection{Key new features}

\begin{description}\itemsep0ex
    \item[Local Earth coordinate frames] In addition to representing celestial
    coordinates, \astropypkg\ now supports specifying positions on the Earth in
    a number of different geocentric systems with the \texttt{EarthLocation}
    class.
    With this, \astropypkg\ now supports Earth-location-specific coordinate
    systems such as the altitude-azimuth (\texttt{AltAz}) or horizontal system.
    Transformations between \texttt{AltAz} and any Barycentric coordinate frame
    also requires specifying a time using the \texttt{Time} class from
    \texttt{astropy.time}.
    With this new functionality, many of the common tasks associated with
    observation planning can now be completed with \astropypkg\ or the
    \astropy-affiliated package \texttt{astroplan} (TODO: cite zenodo entry?).

    \item[Derivatives of coordinate representations]
    As mentioned above, the \texttt{Representation} classes act like
    three-dimensional vectors.
    \texttt{astropy.coordinates} now also supports handling first derivatives of
    the \texttt{Representation} classes through the new \texttt{Differential}
    classes.
    The \texttt{Differential} classes are currently used internal to the
    \texttt{Frame} classes to store velocity data when attached to a
    \texttt{Representation} instance.

    TODO: differential classes. Represent single-derivatives of
    representations. Used to store velocity information, only really useful
    attached to a representation object.

    \item[Proper motion and velocity transformations]
    TODO: Frame classes support proper motions, radial velocities. Explain
    component naming, why SkyCoord doesn't support right now, "experimental" but
    tested feature.

    \item[JPL ephemeris]
    TODO: JPL ephemerids % Who can write this? Erik?
\end{description}
